---
title: "Quick EDA with Crosstab"
author: "Mena WANG"
date: "13/10/2022"
output: 
  html_document:
    toc: false
    toc_float: false

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)

library(here)
library(tidyverse)
library(janitor)

df <- read_csv(here::here("Data","german_credit_data.csv")) #https://www.kaggle.com/datasets/kabure/german-credit-data-with-risk 

df <- df %>% rename(ID = "...1", 
                    credit_risk = Risk)

df <- df %>% 
  janitor::clean_names() 

```


# 💡Quick EDA for feature selection in classification models

Sometimes in machine learning, we would like to get a quick overview of the relationship between the target and all the potential features.  

The problem is, features come in different types and shapes. For example, some features are categorical, some are numerical. Among the numerical ones, some are normally distributed, some aren't. 

Are there any ways to quickly get a big picture of all potential features, despite of all these differences? 

The `crosstable()` function in {crosstable} 📦  may be able to help in such a scenario ~ 

It compares a set of features across the target groups and works well for both categorical and numeric type features. You can easily add a statistical test of group difference for EDA purposes. Tests are automatically chosen depending on the characteristics of the crossed variables (class, size, distribution, etc).

Learn more about the test choice algorithm and the many more options available to tailor-make the table: https://cran.r-project.org/web/packages/crosstable/vignettes/crosstable.html

data source: [German Credit data](https://www.kaggle.com/datasets/kabure/german-credit-data-with-risk)



```{r, echo = FALSE}

german_credit <- df %>% 
  mutate(saving_accounts = as.factor(saving_accounts),
         checking_account = as.factor(checking_account),
         credit_risk = fct_rev(credit_risk)) %>% 
  select(-id,-purpose)

```


```{r}

library(crosstable)

german_credit %>% 
  crosstable(
    german_credit %>% select(-credit_risk) %>% names(), # select all the features
    by = credit_risk, # the target
    percent_digits = 0, percent_pattern = "{n} ({p_col})",
    test = TRUE
    ) %>% 
  as_flextable()

```



